Splitting It Up: The \pkg{spduration} Split-Population Duration Regression Package for Time-varying Covariates

### 2017-10-02 R Journal/beger-hill-metternich-minhas-ward.tex
fixes #4, not sure about #1

\begin{example}
  str(bscoup)
  'data.frame':	5463 obs. of  14 variables:
  $ countryid  : num  909 909 909 909 909 909 909 920 920 920 ...
  $ year       : num  1960 1961 1962 1963 1964 ...
  $ couprisk   : num  0.22 0.22 0.22 0.22 2.57 ...
  $ recentcoups: num  0 0 0 0 1 2 4 0 0 0 ...
  $ rwar       : num  0 0 0 0 0 0 1 0 0 0 ...
  $ milreg     : num  0 0 0 1 0 1 1 0 0 0 ...
  $ wealth     : num  NA NA NA NA NA ...
  $ instab     : num  4 2 9 9 12 13 12 NA 0 4 ...
  $ coup       : Factor w/ 2 levels "no","yes": 1 1 1 2 2 2 1 1 1 1 ...
  $ africa     : num  0 0 0 0 0 0 0 0 0 0 ...
  $ eurnam     : num  0 0 0 0 0 0 0 1 1 1 ...
  $ samerica   : num  0 0 0 0 0 0 0 0 0 0 ...
  $ camerica   : num  0 0 0 0 0 0 0 0 0 0 ...
  $ regconf    : num  0 0 0 0.019 0.019 ...
  - attr(*, "datalabel")= chr ""
  - attr(*, "time.stamp")= chr "30 Jul 2003 12:15"
  - attr(*, "formats")= chr  "%9.0g" "%9.0g" "%9.0g" "%9.0g" ...
  - attr(*, "types")= int  102 102 102 102 102 102 102 102 102 102 ...
  - attr(*, "val.labels")= chr  "" "" "" "" ...
  - attr(*, "var.labels")= chr  "country code .pr89" "year coded" "" "" ...
  - attr(*, "version")= int 7
  - attr(*, "label.table")=List of 1
  ..$ hadcoup: Named int  0 1
  .. ..- attr(*, "names")= chr  "no" "yes"
  bscoup$coup <- ifelse(bscoup$coup == "yes", 1, 0)
  table(bscoup$coup)
  0    1
  5173  290 
\end{example}

@@

@@

The \code{spdur} function is the primary function in the package and
produces a regression model object of class \code{spdur} which can then
be used with further methods. We begin by fitting first a Weibull and
then a log-logistic split-population duration model using the coups
data, including the measure of coup risk in the logit (risk) equation.

\begin{example}
  weib_model <- spdur(
  +    duration ~ milreg + instab + regconf,
  +    atrisk ~ couprisk + wealth + milreg + rwar + regconf + samerica + 
  +      camerica,
  +    data = bscoup, distr = "weib", silent = TRUE)

@@

Using the \code{summary} function on either model object will produce
standard output showing the model formula, estimates for the duration
and risk equations, and test statistics with \(p\)-values. These can be
exported by calling \code{xtable}\citep[see][]{dahl2016xtable} directly on the \code{spdur} object to
produce Table 2.

@@

\bibliography{beger-hill-metternich-minhas-ward}
\newpage
\address{Andreas Beger\\
  Predictive Heuristics\\
  \email{adbeger@gmail.com}}

>>>>

\begin{example}
  str(bscoup)
  'data.frame':	5463 obs. of  14 variables:
  $ countryid  : num  909 909 909 909 909 909 909 920 920 920 ...
  $ year       : num  1960 1961 1962 1963 1964 ...
  $ couprisk   : num  0.22 0.22 0.22 0.22 2.57 ...
  $ recentcoups: num  0 0 0 0 1 2 4 0 0 0 ...
  $ rwar       : num  0 0 0 0 0 0 1 0 0 0 ...
  $ milreg     : num  0 0 0 1 0 1 1 0 0 0 ...
  $ wealth     : num  NA NA NA NA NA ...
  $ instab     : num  4 2 9 9 12 13 12 NA 0 4 ...
  $ coup       : Factor w/ 2 levels "no","yes": 1 1 1 2 2 2 1 1 1 1 ...
  $ africa     : num  0 0 0 0 0 0 0 0 0 0 ...
  $ eurnam     : num  0 0 0 0 0 0 0 1 1 1 ...
  $ samerica   : num  0 0 0 0 0 0 0 0 0 0 ...
  $ camerica   : num  0 0 0 0 0 0 0 0 0 0 ...
  $ regconf    : num  0 0 0 0.019 0.019 ...
  - attr(*, "datalabel")= chr ""
  - attr(*, "time.stamp")= chr "30 Jul 2003 12:15"
  - attr(*, "formats")= chr  "%9.0g" "%9.0g" "%9.0g" "%9.0g" ...
  - attr(*, "types")= int  102 102 102 102 102 102 102 102 102 102 ...
  - attr(*, "val.labels")= chr  "" "" "" "" ...
  - attr(*, "var.labels")= chr  "country code .pr89" "year coded" "" "" ...
  - attr(*, "version")= int 7
  - attr(*, "label.table")=List of 1
  ..$ hadcoup: Named int  0 1
  .. ..- attr(*, "names")= chr  "no" "yes"
\end{example}

@@

\begin{example}
  bscoup$coup <- ifelse(bscoup$coup == "yes", 1, 0)
  table(bscoup$coup)
  0    1
  5173  290 
\end{example}

@@

The \code{spdur} function is the primary function in the package and
produces a regression model object of class \code{spdur} which can then
be used with further methods. We begin by fitting first a Weibull (the default) and
then a log-logistic split-population duration model using the coups
data, including the measure of coup risk in the logit (risk) equation.

\begin{example}
  weib_model <- spdur(
  +    duration ~ milreg + instab + regconf,
  +    atrisk ~ couprisk + wealth + milreg + rwar + regconf + samerica + 
  +      camerica,
  +    data = bscoup, distr = "weibull", silent = TRUE)

@@

Using the \code{summary} function on either model object will produce
standard output showing the model formula, estimates for the duration
and risk equations, and test statistics with \(p\)-values. The estimates are based on maximum likelihood estimation and standard errors are derived using the Hessian matrix of the optimization results. The \code{spdur} parameter estimates can be
exported by calling \code{xtable}\citep[see][]{dahl2016xtable} directly on the \code{spdur} object to
produce Table 2.

@@

\bibliography{beger-hill-metternich-minhas-ward}
\newpage
\address{Andreas Beger\\
  Ward Associates / Predictive Heuristics\\
  Tallinn\\
  Estonia\\
  \email{adbeger@gmail.com}}
